---
title: "Interactive Review Graphics"
author: "Veronica Pagowski"
date: "2024-03-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Big Disjunctions
<style>
body {
    position: absolute;
    left: 0px;
    }
.layout-container {
    display: flex;
    flex-direction: row;
    margin-left: 0px;
}


.graph-container {
    margin: 0px 30px; /* Adjust margin as needed */
    width: 100%;
    padding:0;
}

.graph-container h2 {
    width: 90%;
    top: 220px; 
    font-style: italic; /* Make the font italicized */
    font-size: 20px; /* Set smaller font size */
}

.graph-container h3 {
    width: 90%;
    top: 690px; 
    font-style: italic; /* Make the font italicized */
    font-size: 20px; /* Set smaller font size */
}
</style>


```{r eval =TRUE, echo=FALSE, message = FALSE, warning = FALSE,fig.align = 'left' }
###Associations plots
library(tidyverse)
library(chorddiag)
library(htmlwidgets)
library(gdata)
library(htmltools)
library(gplots)
setwd("~/Desktop/Review")

df<- read.csv("articles_03_24_all.csv", header = TRUE)
df<-df %>% 
  filter(str_detect(Category, pattern = "nogap",negate=TRUE))

############## BIG SPATIAL SCALES ONLY ##############
dfb<-df %>% 
  filter(str_detect(Category, pattern = "Bg,"))

#Get spatial gap matrix
spatial<-dfb %>% 
  filter(str_detect(Category, pattern = "S,") & !str_detect(Category, pattern = "G,"))
out_spatial <- crossprod(table(subset(stack(setNames(lapply(strsplit(spatial$Category, 
                                                                 "[][]|,\\s*"), trimws), spatial$Id))[2:1], nzchar(values))))
diag(out_spatial) <- 0

#Set an order to display categories
custom_order1<-c("V","O","H","I","E","L","B","T","Sx","F","Ox","Sal","W","D","M","U","C","G","S")

#Filter categories that exist in this subset
custom_order_a <- intersect(custom_order1,colnames(out_spatial))

#Arrange 
out_spatial <- out_spatial[custom_order_a, custom_order_a]

#get genetic gap matrix
genetic<-dfb %>% 
  filter(str_detect(Category, pattern = "G,") & !str_detect(Category, pattern = "S,"))
out_gen <- crossprod(table(subset(stack(setNames(lapply(strsplit(genetic$Category, 
                                                                 "[][]|,\\s*"), trimws), genetic$Id))[2:1], nzchar(values))))
diag(out_gen) <- 0

#Arrange 
custom_order_b <- intersect(custom_order1,colnames(out_gen))
out_gen <- out_gen[custom_order_b, custom_order_b]

#get both gap matrix
both <- dfb %>%
  filter(str_detect(Category, pattern = "G,") & str_detect(Category, pattern = "S,"))
out_both <- crossprod(table(subset(stack(setNames(lapply(strsplit(both$Category, 
                                                                 "[][]|,\\s*"), trimws), both$Id))[2:1], nzchar(values))))
diag(out_both) <- 0

#Arrange 
custom_order_c <- intersect(custom_order1,colnames(out_both))
out_both <- out_both[custom_order_c, custom_order_c]

out_spatial[upper.tri(out_spatial)] <- NA
upperTriangle(out_spatial) = lowerTriangle(out_spatial, byrow=TRUE)
out_gen[upper.tri(out_gen)] <- NA
upperTriangle(out_gen) = lowerTriangle(out_gen, byrow=TRUE)
out_both[upper.tri(out_both)] <- NA
upperTriangle(out_both) = lowerTriangle(out_both, byrow=TRUE)

#Make interactive plots
##Spatial
#add white columns that are blank to spatially separate diagram


cols_s <- c("#FFBBFF","#B3EE3A","#D02090","#8B2323","#F0E442","#4169E1","#009E73","#6EE2FF","#B03060","#006400",
            "#8B8B00","#D2B48C","white","white","white","white","white","white","#8B008B","#404040",
            "white","white","white","white","white","white")

ad <- rep(0,12)
out_spatialb2 = cbind(out_spatial[,c(1:12)],ad,ad,ad,ad,ad,ad,out_spatial[,c(13:14)],ad,ad,ad,ad,ad,ad)
out_spatialb2 = rbind(out_spatialb2[c(1:12),],ad,ad,ad,ad,ad,ad,out_spatialb2[c(13:14),],ad,ad,ad,ad,ad,ad)

p1 <- chorddiag(out_spatialb2, groupColors = cols_s, showGroupnames = FALSE,groupPadding = 2,showTooltips = TRUE,showZeroTooltips = FALSE,tickInterval=10,ticklabelFontsize=0,precision=3,groupnamePadding = 0,width = 350, height=350, margin=10)

##Genetic
#add white columns that are blank to spatially separate diagram
cols_gb <- c("#FFBBFF","#B3EE3A","#D02090","#D2B48C", "white","white","white","white","white","white","#00008B","white","white","white","white","white","white")
ad <- rep(0,4)
out_genb2 = cbind(out_gen[,c(1:4)],ad,ad,ad,ad,ad,ad,out_gen[,c(5)],ad,ad,ad,ad,ad,ad)
out_genb2 = rbind(out_genb2[c(1:4),],ad,ad,ad,ad,ad,ad,out_genb2[c(5),],ad,ad,ad,ad,ad,ad)

p2 <- chorddiag(out_genb2, groupColors = cols_gb, showGroupnames = FALSE,groupPadding = 2,showTooltips = TRUE,showZeroTooltips = FALSE,tickInterval=10,ticklabelFontsize=0,precision=3,groupnamePadding = 0,width = 350, height=350, margin=10)
#q

#Both
cols_b <- c("#FFBBFF","#B3EE3A","#D02090","#8B2323","#F0E442", "#3A5FCD", "#CD5555","#009E73","#FFA07A","#6EE2FF","#006400", "#8B8B00","#D2B48C", "white","white","white","white","white","white","#00008B","#404040","white","white","white","white","white","white")

ad <- rep(0,13)
out_bothb2 = cbind(out_both[,c(1:13)],ad,ad,ad,ad,ad,ad,out_both[,c(14:15)],ad,ad,ad,ad,ad,ad)
out_bothb2 = rbind(out_bothb2[c(1:13),],ad,ad,ad,ad,ad,ad,out_bothb2[c(14:15),],ad,ad,ad,ad,ad,ad)

p3 <- chorddiag(out_bothb2, groupColors = cols_b, showGroupnames = FALSE,groupPadding = 2,showTooltips = TRUE,showZeroTooltips = FALSE,tickInterval=10,ticklabelFontsize=0, precision=3,groupnamePadding = 0,width = 350, height=350, margin=10)


# Define titles for each graph
title_p1 <- "Spatial"
title_p2 <- "Genetic"
title_p3 <- "Both"

# Create div layout with custom CSS and titles
layout <- tags$div(
  class = "layout-container",
  tags$div(
    class = "graph-container",
    tags$h2(title_p1),  # Add title for graph p1
    p1
  ),
  tags$div(
    class = "graph-container",
    tags$h2(title_p2),  # Add title for graph p2
    p2
  ),
  tags$div(
    class = "graph-container",
    tags$h2(title_p3),  # Add title for graph p3
    p3
  )
)
layout
#setwd("/Users/veronicapagowski/Desktop/interactive_app/interactive_review")
#saveWidget(p, "chord_test2.html", selfcontained = TRUE, knitrOptions = list())

```


## Small Disjunctions
```{r eval =TRUE, echo=FALSE, message = FALSE, warning = FALSE }

############## SMALL SPATIAL SCALES ONLY ##############
dfs<-df %>% 
  filter(str_detect(Category, pattern = "Sm,"))

#Get spatial gap matrix
spatial1<-dfs %>% 
  filter(str_detect(Category, pattern = "S,") & !str_detect(Category, pattern = "G,"))
out_spatial1 <- crossprod(table(subset(stack(setNames(lapply(strsplit(spatial1$Category, 
                                                                 "[][]|,\\s*"), trimws), spatial1$Id))[2:1], nzchar(values))))
diag(out_spatial1) <- 0

#Set an order to display categories
custom_order1<-c("V","O","H","I","E","L","B","T","Sx","F","Ox","Sal","W","D","M","U","C","G","S")

#Filter categories that exist in this subset
custom_order_a <- intersect(custom_order1,colnames(out_spatial1))

#Arrange 
out_spatial1 <- out_spatial1[custom_order_a, custom_order_a]

#get genetic gap matrix
genetic1<-dfs %>% 
  filter(str_detect(Category, pattern = "G,") & !str_detect(Category, pattern = "S,"))
out_gen1 <- crossprod(table(subset(stack(setNames(lapply(strsplit(genetic1$Category, 
                                                                 "[][]|,\\s*"), trimws), genetic1$Id))[2:1], nzchar(values))))
diag(out_gen1) <- 0

#Arrange 
custom_order_b <- intersect(custom_order1,colnames(out_gen1))
out_gen1 <- out_gen1[custom_order_b, custom_order_b]

#get both gap matrix
both1 <- dfs %>%
  filter(str_detect(Category, pattern = "G,") & str_detect(Category, pattern = "S,"))
out_both1 <- crossprod(table(subset(stack(setNames(lapply(strsplit(both1$Category, 
                                                                 "[][]|,\\s*"), trimws), both1$Id))[2:1], nzchar(values))))
diag(out_both1) <- 0

#Arrange 
custom_order_c <- intersect(custom_order1,colnames(out_both1))
out_both1 <- out_both1[custom_order_c, custom_order_c]

out_spatial1[upper.tri(out_spatial1)] <- NA
upperTriangle(out_spatial1) = lowerTriangle(out_spatial1, byrow=TRUE)
out_gen1[upper.tri(out_gen1)] <- NA
upperTriangle(out_gen1) = lowerTriangle(out_gen1, byrow=TRUE)
out_both1[upper.tri(out_both1)] <- NA
upperTriangle(out_both1) = lowerTriangle(out_both1, byrow=TRUE)

#Make interactive plots

##Spatial

cols_s <- c("#FFBBFF","#B3EE3A","#D02090","#8B2323","#F0E442", "#3A5FCD", "#CD5555","#009E73","#FFA07A","#6EE2FF","#B03060",
           "#EE3B3B", "#FF7F24","#006400", "#8B8B00","#D2B48C", "white","white","white","white","white","white",
           "#8B008B","#404040","white","white","white","white","white","white")

ad <- rep(0,16)
out_spatial2 = cbind(out_spatial1[,c(1:16)],ad,ad,ad,ad,ad,ad,out_spatial1[,c(17:18)],ad,ad,ad,ad,ad,ad)
out_spatial2 = rbind(out_spatial2[c(1:16),],ad,ad,ad,ad,ad,ad,out_spatial2[c(17:18),],ad,ad,ad,ad,ad,ad)

p1s <- chorddiag(out_spatial2, groupColors = cols_s, showGroupnames = FALSE,groupPadding = 2,showTooltips = TRUE,showZeroTooltips = FALSE,precision=3,tickInterval=10,ticklabelFontsize=0,groupnamePadding = 0,width = 350, height=350, margin=10)


##Genetic
#add white columns that are blank to spatially separate diagram
cols_g <- c("#FFBBFF","#B3EE3A","#D02090","#8B2323","#F0E442", "#3A5FCD", "#CD5555","#009E73","#FFA07A","#6EE2FF",
            "#EE3B3B", "#FF7F24","#006400", "#8B8B00","#D2B48C", "white","white","white","white","white","white",
           "#8B008B","#00008B","white","white","white","white","white","white")

ad <- rep(0,15)
out_gen2 = cbind(out_gen1[,c(1:15)],ad,ad,ad,ad,ad,ad,out_gen1[,c(16:17)],ad,ad,ad,ad,ad,ad)
out_gen2 = rbind(out_gen2[c(1:15),],ad,ad,ad,ad,ad,ad,out_gen2[c(16:17),],ad,ad,ad,ad,ad,ad)

p2s <- chorddiag(out_gen2, groupColors = cols_g, showGroupnames = FALSE,groupPadding = 2,showTooltips = TRUE,precision=3,showZeroTooltips = FALSE,tickInterval=10,ticklabelFontsize=0,groupnamePadding = 0,width = 350, height=350, margin=10)

#Both
cols_b <- c("#FFBBFF","#B3EE3A","#D02090","#8B2323", "#3A5FCD", "#CD5555","#009E73","#FFA07A","#6EE2FF","#B03060",
             "#FF7F24","#006400", "#8B8B00","#D2B48C", "white","white","white","white","white","white",
           "#8B008B","#00008B","#404040","white","white","white","white","white","white")

ad <- rep(0,14)
out_both2 = cbind(out_both1[,c(1:14)],ad,ad,ad,ad,ad,ad,out_both1[,c(15:17)],ad,ad,ad,ad,ad,ad)
out_both2 = rbind(out_both2[c(1:14),],ad,ad,ad,ad,ad,ad,out_both2[c(15:17),],ad,ad,ad,ad,ad,ad)

p3s <- chorddiag(out_both2, groupColors = cols_b, showGroupnames = FALSE, groupPadding = 2,showTooltips = TRUE,precision=3, showZeroTooltips = FALSE,tickInterval=10,ticklabelFontsize=0,groupnamePadding = 0,width = 350, height=350, margin=10)


# Define titles for each graph
title_p1 <- "Spatial"
title_p2 <- "Genetic"
title_p3 <- "Both"

# Create div layout with custom CSS and titles
layout2 <- tags$div(
  class = "layout-container",
  tags$div(
    class = "graph-container",
    tags$h3(title_p1),  # Add title for graph p1
    p1s
  ),
  tags$div(
    class = "graph-container",
    tags$h3(title_p2),  # Add title for graph p2
    p2s
  ),
  tags$div(
    class = "graph-container",
    tags$h3(title_p3),  # Add title for graph p3
    p3s
  )
)
layout2
#setwd("/Users/veronicapagowski/Desktop/interactive_app/interactive_review")

```

